Characterization of gaps in directly bonded Si compound optics

### 2014-04-21 AO_bondedSi.tex
tweak MGS edits in intro, etc

While it is possible that proper precautions to eliminate all micron-sized particles from both Si surfaces prior to bonding, the power-law nature of the particle size distribution in clean-room environments \cite{doi:10.1080/02786828608959094} means that it is significantly more difficult to assure that no particles of the 10$-$60 nm size scale are present.  Small particles could be a concern if they act as "tent poles", that create gaps where the bonding is incomplete (Figure \ref{figParticle}).  Some authors \cite{1991JaJAP..30..615M, 1992JEMat..21..669M, 1989JaJAP..28L2141L, Mitani1990} have referred to these large ($\sim$ 1 $\mu$m size) gaps as \emph{IR bubbles}, or simply bubbles, owing to their appearance in infrared (IR) transmission images as contiguous regions of a deficit of IR transmission.  The gaps have also been referred to as voids\cite{2000RScI...71.1869G}, interfacial voids, or gaps.  In this paper we will reserve the term ``IR bubbles'' for gaps that are large enough to be detected directly in conventional IR imaging.  The term ``gap'' will apply more broadly to any finite size gap, exceeding the scale over which interfacial molecular forces are acting, roughly $>$2 nm.  We omit the adjective ``interfacial'' before gap for simplicity.

@@

\begin{figure}[htbp]
\centerline{\includegraphics[width=0.65\columnwidth]{figs/20140421_absolute.pdf}}
\caption{Modeled absolute transmission through a silicon substrate with no gap (top black solid curve), and small gaps of axial extent 20 nm (red dashed curve) and 35 nm (cyan triple-dot dashed curve)\label{figAbsoluteTrans}.  The absolute transmission through Si depends on the Si refractive index, which depends on wavelength. }
\end{figure}

@@

\begin{figure}[htbp]
\centerline{\includegraphics[width=0.65\columnwidth]{figs/20140421_absoluteC.pdf}}
\caption{Modeled etalon transmission through a silicon substrate with gaps of axial extent 35 nm (red dotted curve), 350 nm (green dash-dot curve), and 3500 nm (blue long-dashed curve)\label{figEtalonRelTrans}.  The curves are examples from a family defined in Equation \ref{eqFP}.  The 3500 nm gap curve has obvious Fabry-P\`erot fringes, whereas the 35 and 350 nm gap curves vary smoothly with wavelength.  }
\end{figure}

>>>>

While it is possible that proper precautions can be made to eliminate all micron-sized particles from both Si surfaces prior to bonding, the power-law particle size distribution in clean-room environments \cite{doi:10.1080/02786828608959094} means that it is significantly more difficult to assure that no particles of the 10$-$60 nm size scale are present.  Small particles could be a concern if they act as ``tent poles", that create gaps where the bonding is incomplete (Figure \ref{figParticle}).  Some authors \cite{1991JaJAP..30..615M, 1992JEMat..21..669M, 1989JaJAP..28L2141L, Mitani1990} have referred to these large ($\sim$ 1 $\mu$m size) gaps as \emph{IR bubbles}, or simply bubbles, owing to their appearance in infrared (IR) transmission images as contiguous regions of a deficit of IR transmission.  The gaps have also been referred to as voids\cite{2000RScI...71.1869G}, interfacial voids, or gaps.  In this paper we will reserve the term ``IR bubbles'' for gaps that are large enough to be detected directly in conventional IR imaging.  The term ``gap'' will apply more broadly to any finite size gap, exceeding the scale over which interfacial molecular forces are acting, roughly $>$2 nm.  We omit the adjective ``interfacial'' before gap for simplicity.

@@

%The following 3 figures were made with fabry_perot_Si_20140421.pro and other variants.
\begin{figure}[htbp]
\centerline{\includegraphics[width=0.65\columnwidth]{figs/20140421_absolute.pdf}}
\caption{Modeled absolute transmission through a silicon substrate with no gap (top black solid curve), and small gaps of axial extent 20 nm (red dashed curve) and 35 nm (cyan triple-dot dashed curve)\label{figAbsoluteTrans}.  The absolute transmission through Si depends on the Si refractive index, which depends on wavelength. }
\end{figure}

@@

\begin{figure}[htbp]
\centerline{\includegraphics[width=0.65\columnwidth]{figs/20140421_absoluteC.pdf}}
\caption{Modeled etalon transmission through a silicon substrate with gaps of axial extent 35 nm (red dotted curve), 350 nm (green dash-dot curve), and 3500 nm (blue long-dashed curve)\label{figEtalonRelTrans}.  The curves are examples from a family defined in Equation \ref{eqFP}.  The 3500 nm gap curve has obvious Fabry-P\`erot fringes, whereas the 35 and 350 nm gap curves vary smoothly with wavelength.} 
\end{figure}
